%\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}
\pagenumbering{gobble}

Surgical planning is routinely applied to increase the success ratio and reduce the adverse events in complex surgeries. In order to properly plan the intervention, the surgeon needs a model of the target anatomical location with enough details so that he can quickly understand how a particular decision will affect the outcome of the entire surgery. In this work we will focus on the creation of surgical planning systems for fetal and brain surgery. 

The application on fetal surgery is centered on \textit{twin-twin transfusion syndrome (TTTS) }-which can be fatal if left untreated- and extraction of vascular network on the surface of the placenta. Unfortunately, this is a difficult problem due to limited image quality and high variability in the position and orientation of the placenta and the low visibility of vessel in MRI images. In this work we present a software for the estimation of patient specific fetoscope insertion path for use in TTTS, in order to improve and optimize the surgical workflow coming into surgery.

 The application on \textit{Deep Brain Stimulation (DBS)} is centered on modeling and activation of bilateral subthalamic nucleus (B-STN) which is a safe and effective procedure for the treatments of the motor symptoms of advanced Parkinson Disease (PD). The software allows to plan the insertion trajectory of the neurostimulator as well as simulating the stimulation on the targeted brain area. By doing so, we can plan the insertion route safely in a simulated, safe environment, and preview the effects of the stimulation in the selected placement point, to assess if the stimulation will cover the required area or will spread to unwanted, non-targeted areas.




\newpage
\end{abstract}